Plots

### 2025-02-25 src/plots.Rmd
Add plot adjustments

# Plot performance of models
plot_perf <- function(
        df_long,
        f = calc_pccc,
        group = "cod_name",
        title = NULL,
        x_title = NULL,
        y_title = NULL,
        text_mid_size = 2,
        text_end_size = 3,
        text_hjust = 0.2,
        x_limits = c(0, 1),
        ...
    ) {

@@

    # Plot metric for each model
    out <- ggplot(df_plot, aes(x = metric, y = .data[[group]])) +
        geom_point( # mid points
            data = df_mids,
            color = "gray60",
            size = 1
        ) +
        geom_point (# min points
            data = df_ends,
            aes(x = min_metric),
            size = 1.5
        ) +
        geom_point (# max points
            data = df_ends,
            aes(x = max_metric),
            size = 1.5
        ) +
        geom_segment( # min max lines
            data = df_ends,
            aes(
                x = min_metric,
                xend = max_metric,
                y = .data[[group]],
                yend = .data[[group]]
            ),
            linewidth = 0.75
        ) +
        geom_text( # min model text
            data = df_ends,
            aes(
                x = min_metric,
                y = .data[[group]],
                label = paste0(model_min, " (", round(min_metric, 2), ")")
            ),
            hjust = 1 + text_hjust,
            vjust = 0.5,
            size = text_end_size
        ) +
        geom_text( # max model text
            data = df_ends,
            aes(
                x = max_metric,
                y = .data[[group]],
                label = paste0(model_max, " (", round(max_metric, 2), ")")
            ),
            hjust = 0 - text_hjust,
            vjust = 0.5,
            size = text_end_size
        ) +
        geom_text_repel( # mid model text
            data = df_mids,
            aes(label = model_label),
            color = "gray60",
            max.overlaps = Inf,
            size = text_mid_size
        ) +
        scale_x_continuous(
            limits = x_limits,
            expand = expansion(add = 0.2)
        ) +
        labs(
            title = title,
            x = x_title,
            y = y_title
        ) +
        theme_minimal() +
        theme(
            panel.border = element_rect(
                color = "black",
                fill = NA,
                linewidth = 0.5
            ),
            legend.position = "none",
            panel.grid.major = element_blank(),
            panel.grid.minor = element_blank()
        )
    return(out)
}

@@

@@

@@

# Plot perf for pccc
plot_perf(
    df_long %>% filter(age == "adult"),
    calc_pccc,
    title = paste0(cod_adult, " Causes of Death for ", n_adult, " Adult Records")
) /
    plot_perf(
        df_long %>% filter(age == "child"),
        calc_pccc,
        title = paste0(cod_child, " Causes of Death for ", n_child, " Child Records")
    ) /
    plot_perf(
        df_long %>% filter(age == "neo"),
        calc_pccc,
        title = paste0(cod_neo, " Causes of Death for ", n_neo, " Neonatal Records")
    ) +
    plot_layout(heights = c(2, 1, 1))

@@

### CSMF Accuracy

>>>>

# Plot performance of models
plot_perf <- function(
        df_long,
        f = calc_pccc,
        group = "cod_name",
        title = NULL,
        x_title = NULL,
        y_title = NULL,
        text_mid_size = 2,
        text_mid_vjust = 2.5,
        text_end_size = 3,
        text_hjust = 0.2,
        add_min_points = F,
        add_max_points = F,
        mid_points_size = 1.5,
        min_points_size = 2,
        max_points_size,
        x_limits = c(0, 1),
        ...
    ) {

@@

    # Plot metric for each model
    out <- ggplot(df_plot, aes(x = metric, y = .data[[group]])) +
        geom_point( # mid points
            data = df_mids,
            size = mid_points_size
        ) +
        geom_segment( # min max lines
            data = df_ends,
            aes(
                x = min_metric,
                xend = max_metric,
                y = .data[[group]],
                yend = .data[[group]]
            ),
            linewidth = 0.75
        ) +
        geom_text( # min model text
            data = df_ends,
            aes(
                x = min_metric,
                y = .data[[group]],
                label = paste0(model_min, " (", round(min_metric, 2), ")")
            ),
            hjust = 1 + text_hjust,
            vjust = 0.5,
            size = text_end_size
        ) +
        geom_text( # max model text
            data = df_ends,
            aes(
                x = max_metric,
                y = .data[[group]],
                label = paste0(model_max, " (", round(max_metric, 2), ")")
            ),
            hjust = 0 - text_hjust,
            vjust = 0.5,
            size = text_end_size
        ) +
        geom_text_repel( # mid model text
            data = df_mids,
            aes(label = model_label),
            color = "gray60",
            vjust = text_mid_vjust,
            max.overlaps = Inf,
            size = text_mid_size
        ) +
        scale_x_continuous(
            limits = x_limits,
            expand = expansion(add = 0.2)
        ) +
        labs(
            title = title,
            x = x_title,
            y = y_title
        ) +
        theme_minimal() +
        theme(
            panel.border = element_rect(
                color = "black",
                fill = NA,
                linewidth = 0.5
            ),
            legend.position = "none",
            panel.grid.major = element_blank(),
            panel.grid.minor = element_blank()
        )

    # Add min and max points
    if (add_min_points) {
        out <- out + geom_point( # min points
            data = df_ends,
            aes(x = min_metric),
            size = 2
        )
    }
    if (add_max_points) {
        out <- out + geom_point( # max points
            data = df_ends,
            aes(x = max_metric),
            size = 2
        )
    }
    return(out)
}

@@

## Age Case Count

Count the number and percentage of cases for each age group.

@@

## PCCC By Age

```{r}
plot_perf(
    df_long,
    calc_pccc,
    group = "age_name",
    x_title = "Partial Chance Corrected Concordance (PCCC)",
    y_title = "Cause of Death",
    text_mid_size = 2.5,
    text_mid_vjust = 3
)
```

@@

# Plot perf for pccc
plot_perf(
    df_long %>% filter(age == "adult"),
    calc_pccc,
    group = "cod_name",
    title = paste0("(a) Adult Records (n=", n_adult, ")"),
    x_title = "Partial Chance Corrected Concordance (PCCC)",
    y_title = "Cause of Death"
) /
    plot_perf(
        df_long %>% filter(age == "child"),
        calc_pccc,
        group = "cod_name",
        title = paste0("(b) Child Records (n=", n_child, ")"),
        x_title = "Partial Chance Corrected Concordance (PCCC)",
        y_title = "Cause of Death"
    ) /
    plot_perf(
        df_long %>% filter(age == "neo"),
        calc_pccc,
        group = "cod_name",
        title = paste0("(c) Neonatal Records (n=", n_child, ")"),
        x_title = "Partial Chance Corrected Concordance (PCCC)",
        y_title = "Cause of Death"
    ) +
    plot_layout(
        heights = c(2, 1, 1),
        axis_titles = "collect"
    )

@@

## CSMF Accuracy
